\documentclass[varwidth]{standalone}

\begin{document}


\section{3Sum (P015)}
\subsection{Based on Two Sum}
First idea is based on 001.Two Sum. It's rather intuitive.
Since two sum can get two number with target sum,
if we set the target as the negative of $\mathtt{nums[i]}$,
and get another two number $\mathtt{nums[j]}$ and $\mathtt{nums[k]}$ with sum of
$-\mathtt{nums[i]}$, we automatically get a triplet with sum of
$\mathtt{nums[i]} + \mathtt{nums[j]} + \mathtt{nums[k]} = 0$.
We can repeat the process for all number in the array to get all the possible
triplets. The running time is intuitively $\mathcal{O}(n^2)$,  since two sum take
$\mathcal{O}(n)$ and was repeated $n$ times.

To simplify the operation of duplicating number, we may sort the array first.
Since sorting takes $\mathcal{O}(n \log n)$ time, less than $\mathcal{O}(n^2)$,
sorting time can be discard.

Although the solution is after all $\mathcal{O}(n^2)$, the overall running time
is unacceptably slow, with my C implementation.

The main reason is to simplify the hash function, I let the index equals to the
number itself plus a rather big number, so that even negative number can
directly map into an array. The big number is unfortunately set to $100000$.
And to check the existance of an integer, the condition became
\lstinline[language=c]{if (h[x + IMAX + 1] != 0)}.
Therefore, each time hash table was accessed, it must move at least $100000$ to
get the hash value, greatly consuming time without any alarm.

\subsection{Two Pointers}
Although previous solution used solution for two sum, it failed to see another
chance to reduce time and space.
\begin{quote}
    \emph{The array is sorted in the first step.}
\end{quote}

An sorted array is each to manipulate.
We can still use the idea of turning three sum into two sum, but when dealing
with sorted array, two sum can easily implemented using two pointers

Let two pointers \texttt{i j} start at each side, where $i < j$.
For a given $target$, if $\mathtt{nums[i]} + \mathtt{nums[j]} < target$.
We can move $i$ rightward to increase the sum of the two.
Or on the other hand if $\mathtt{nums[i]} + \mathtt{nums[j]} > target$.
We can move $j$ leftward to decrease the sum of the two.
Until otherwise, if $\mathtt{nums[i]} + \mathtt{nums[j]} = target$, we
found one answer, or $i > j$, there is no possible answer.

The biggest advantage is this solution does not use hash table. Only traverse
through the array is enough to get all possible answers.

\end{document}
