\section{Greedy Algorithm}

\subsection{Greedy in a Glance}

Greedy Algorithm is repeatedly taking locally optimal step in
hopes reaching global optimal solution.

Often Greedy is WRONG!

So we should assume greedy is wrong, unless proven otherwise.

However, if we can prove greedy works in some circumstance,
it would be a simple and fast solution in most cases.

\subsection{Greedy Class Scheduling}
\subsubsection{Description of Problem}

Target: On given day of week, we want to take as many classes as possible.
Constraint: We cannot take two classes whose times overlap.

\AlgoInput Given $S[1 \ldots n]$ and $F[1 \ldots n]$, which 
\[S[i] = \text{start time of class} i \]
\[F[i] = \text{finish time of class} i \]

\AlgoOutput Select largest subset $X \subseteq \{1 \ldots n \}$,
s.t. for $i \neq j \in X$ either $S[i] > F[j]$ or $S[j] > F[i]$.

\subsubsection{Analysis}
Recursive approach: consider class 1.
\[B_4 = \{ i | 2 \leq i \leq n \text{ and } F[i] < S[1] \}\]
\[L_8 = \{ i | 2 \leq i \leq n \text{ and } S[i] > F[1] \}\]

DP approach: \bigO{n} running time.

But we can do better with greedy: Pick class which finishes first.

In other word, the algorithm is:
\begin{quote}
    Scan classes in increasing order of finishing time.
    Each time encounter non-conflicting class, select it.
\end{quote}
as described in \cref{greedy_class_scheduling}.

\begin{algorithm}[H]
    \caption{Greedy Solution for Class Scheduling}\label{greedy_class_scheduling}
    \begin{algorithmic}[1]
        \Procedure{GreedySchedule}{$S[1 \ldots n]$, $F[1 \ldots n]$}
            \State Sort $F$ and permute $S$ to match.
            \State $count = 1$
            \State $X[count] = 1$ \Comment{$X[1 \ldots n]$}
            \For{$i = 2 \text{ to } n$}
                \If{$S[i] > F[X[count]]$}
                    \State $count = count + 1$
                    \State $X[count] = i$
                \EndIf
            \EndFor
            \Return $X[1 \ldots count]$
        \EndProcedure
    \end{algorithmic}
\end{algorithm}

Running time: $\Theta(n \log n) \rightarrow $ sorting running time.

\subsubsection{Proof}
Note that there may be many optimal solutions.
And Greedy produces unique solution.
So we cannot argue any optimal solution looks like greedy.

\begin{lemma}
At least one optimal solution include class that finishes first.
\end{lemma}

\begin{proof}
    Let $f$ be class that finishes first, $X$ be an optimal set of classes.
    If $f \in X$ then lemma proven.
    Otherwise, $f \notin X$. Let $g$ be class in $X$ that finishes first.
    Since $f$ finishes before $g$, $f$ cannot conflict with any class in $X \setminus \{g\}$

    Thus $X^\prime = X \cup \{f\} \setminus \{g\}$ is a valid solution with max size and contain $f$.
\end{proof}

\begin{theorem}
    Greedy schedule is optimal.\footnote{Can be proved using induction}
\end{theorem}

\begin{proof}
    Let $f$ be class that finishes first. $L$ is set that starts after $f$ finishes.
    Best schedule containing $f$ is optimal. This best schedule must be optimal on $L$.
    $L$ is strictly smaller set of classes, so can apply induction.
\end{proof}

\subsection{General Prove Method for Greedy Algorithm: Exchange Argument}
\begin{enumerate}
    \item Assume there is a optimal solution other than greedy algorithm.
    \item Fine the ``first'' difference between it and greedy algorithm.
    \item Argue can exchange optimal choice for greedy one, without degrading solution value.
\end{enumerate}

\subsection{Huffman Codes}
\subsubsection{Description of Problem}
\AlgoInput Given an alphabet $\Sigma$.

\AlgoOutput A binary code for $\Sigma$ maps
every $x \in \Sigma$ to a unique binary string.


\AlgoExample
Fixed length codes: Map $\Sigma$ to strings all having same length.

Given Alphabet: $\Sigma = \{a, b, c, d, e, f\}$

Frequency for each character $F = \{45, 13, 12, 16, 9, 5\}$.

\begin{align*}
    a &= 000 & b &= 001 & c &= 010 \\
    d &= 011 & e &= 100 & f &= 101
\end{align*}

\begin{figure}[H]
    \caption{Binary Code Tree for Fixed Length Codes}
    \centering
\begin{tikzpicture}[every tree node/.style={draw=none}, level distance=1.5cm, sibling distance=1cm]
    \Tree [.100
        \edge node [auto, swap] {0}; [.86
            \edge node [auto, swap] {0}; [.58
                \edge node [auto, swap] {0}; [.45
                    \edge[n] node {$\Uparrow$}; [.\node[n]{a}; ]
                ]
                \edge node [auto] {1}; [.13
                    \edge[n] node {$\Uparrow$}; [.\node[n]{b}; ]
                ]
            ]
            \edge node [auto] {1}; [.28
                \edge node [auto, swap] {0}; [.12
                    \edge[n] node {$\Uparrow$}; [.\node[n]{c}; ]
                ]
                \edge node [auto] {1}; [.16
                    \edge[n] node {$\Uparrow$}; [.\node[n]{d}; ]
                ]
            ]
        ]
        \edge node [auto] {1}; [.14
            \edge node [auto, swap] {0}; [.14
                \edge node [auto, swap] {0}; [.9
                    \edge[n] node {$\Uparrow$}; [.\node[n]{e}; ]
                ]
                \edge node [auto] {1}; [.5
                    \edge[n] node{$\Uparrow$}; [.\node[n]{f}; ]
                ]
            ]
            \edge[n]; [.\node[n]{ }; ]
        ]
    ]
\end{tikzpicture}
\par
\end{figure}

The length of coded files:
\begin{align*}
    &3 \times 45 + 3 \times 13 + 3 \times 12 + 3 \times 14 + 3 \times 16 + 3 \times 9 + 3 \times 5 \\
    &= \sum F[i] \times depth(i)
\end{align*}


What if the codes is not fixed length?

\begin{align*}
    a &= 0 & b &= 101 & c &= 100 \\
    d &= 111 & e &= 1101 & f &= 1100
\end{align*}

\begin{figure}[H]
    \caption{Binary Code Tree for Not Fixed Length Codes}
    \centering
\begin{tikzpicture}[every tree node/.style={draw=none}, level distance=1.5cm, sibling distance=1cm]
    \Tree [.100
        \edge node [auto, swap] {0}; [.45
            \edge[n] node {$\Uparrow$}; [.\node[n]{a}; ]
        ]
        \edge node [auto] {1}; [.55
            \edge node [auto, swap] {0}; [.25
                \edge node [auto, swap] {0}; [.12
                    \edge[n] node {$\Uparrow$}; [.\node[n]{c}; ]
                ]
                \edge node [auto] {1}; [.13
                    \edge[n] node {$\Uparrow$}; [.\node[n]{b}; ]
                ]
            ]
            \edge node [auto] {1}; [.30
                \edge node [auto, swap] {0}; [.14
                    \edge node [auto, swap] {0}; [.5
                        \edge[n] node {$\Uparrow$}; [.\node[n]{f}; ]
                    ]
                    \edge node [auto] {1}; [.9
                        \edge[n] node {$\Uparrow$}; [.\node[n]{e}; ]
                    ]
                ]
                \edge node [auto] {1}; [.16
                    \edge[n] node {$\Uparrow$}; [.\node[n]{d}; ]
                ]
            ]
        ]
    ]
\end{tikzpicture}
\end{figure}

The length of coded files:
\begin{align*}
    & 1 \times 45 + 3 \times 13 + 3 \times 12 + 3 \times 16 + 4 \times 9 + 4 \times 5 \\
    &= 224
\end{align*}

Note that, in order to decode, the codes need to be prefix-free, i.e. no code word
is a prefix of another, which means characters must at leaves.

So here comes the greedy algorithm: Huffman Codes.

\subsubsection{Definition}

\AlgoInput Alphabet $\Sigma$ of size $n$ and the frequency array $F[1 \ldots n]$,
$F[i]$ is the frequency of character $\Sigma[i]$.

\AlgoOutput Find a prefix free tree, s.t. $\displaystyle\sum{F[i]\times depth(i)}$ minimized.

\vspace{0.1in}
\noindent \textbf{Huffman Algorithm:} Recursively merge two least frequent.

\subsubsection{Analysis}

\begin{claim}
    Huffman's Algorithm is optimal.
\end{claim}

\observation Optimal code trees are full binary tree (gbt\footnote{Definition is in homework 1.}).
In other word, leaf at maximum depth has a sibling.

\begin{lemma}
    Let $x$ and $y$ be two least frequent characters. There is an optimal tree
    where $x,y$ are siblings.
\end{lemma}

\begin{proof} Let $T$ be an optimal tree of depth $d$.

By observation, there are siblings $a$, $b$ at depth $d$.
If $a = x$ and $b = y$, then proved.

Let $T^\prime$ be the tree obtained by swapping $x$ and $a$.

Then the depth of $x$ increased by $d - depth(x,T) = z$, and
the depth of $a$ decreased by $z$, so,
\[Cost(T^\prime) = Cost(T) - (F[a]-F[x])\times z\]
where $x$ was least frequent. Thus
\[F[a] -F[x] \geq 0 \Rightarrow Cost(T^\prime) \leq Cost(T)\]

Based on assumption, $T$ is a optimal tree, so $Cost(T) \leq Cost(T^\prime)$.

Hence, $T$ equals to $T^\prime$
\end{proof}

\begin{theorem}
Huffman codes is optimal.
\end{theorem}

\begin{proof}
Assume $F[1]$, $F[2]$ is least frequent. Define $F[n+1] = F[1] + F[2]$.

Let $T^\prime$ be the Huffman tree on $F[3 \ldots n+1]$,
$T$ be the Huffman tree on $F[1 \ldots n]$ obtained from $T^\prime$ by
replacing $n+1$ with $1$ and $2$.

For any prefix tree $\overline{T}$ obtained from any $\overline{T^\prime}$
on $F[3 \ldots n+1]$ by replacing $n+1$ with $1$ and $2$ can prove
\[Cost(\overline{T}) = Cost(\overline{T^\prime}) + F[1] + F[2]\]

\noindent Use Induction:

\BaseCase For one or two characters, Huffman is optimal.
Now want to prove Huffman tree $T$ is optimal.

\InductionStep Assume $T^\prime$ is an optimal tree, then
$Cost(\overline{T}) = Cost(\overline{T^\prime}) + F[1] + F[2]$,
which means minimizing $Cost(\overline{T})$ is equivalent
to minimizing $Cost(\overline{T^\prime})$.

$T$ is optimal among trees on $\Sigma[1 \ldots n]$ obtained by an expanding $n+1$
node to $1$ and $2$ from an optimal tree on $F[3 \ldots n+1]$.

In conclusion, Huffman is optimal.
\end{proof}

Greedy Ends Here.
